Association between SARS-CoV-2 and metagenomic content of samples from the Huanan Seafood Market

### 2023-05-02 paper/paper.tex
add new tables

@@

species      &   sample              & \makecell[r]{mitochondrial \\ reads from \\ species} &  \makecell[r]{reads \\ aligning \\ to SARS2} & \makecell[r]{ total pre-\\processed \\ reads} \\ 

@@

 Overall, there were SARS-CoV-2 reads in just 3 of the 28 samples with at least 20\% of their chordate mitochondrial composition from the non-human susceptible species thought to have been sold live in the market (Table~\ref{tab:susceptible}).
There were 14 samples with at least 20\% chordate mitochondrial composition from raccoon dogs, but only sample Q61 contained any SARS-CoV-2 reads (1 of $\sim2.1 \times 10^8$ high-quality reads).
None of the six samples with at least 20\% chordate mitochondrial composition from bamboo rats contained any SARS-CoV-2 reads.
There was one sample each with at least 20\% chordate mitochondrial composition from Amur hedgehog and Malayan porcupine that contained SARS-CoV-2 reads (Table~\ref{tab:susceptible}).

@@

>>>>

See Table~\ref{tab:susceptible_mammal} for a similar table that shows mammalian rather than chordate composition.
This table uses a 20\% cutoff due to space considerations; to see similar data tabulated for all samples with no cutoff, see the much larger Table~\ref{tab:raccoon_dog_long} (for raccoon dog) and Table~\ref{tab:mito_composition_by_sample} (for all species).

@@

species      &   sample              & \makecell[r]{chordate \\ mitochondrial \\ reads from \\ species} &  \makecell[r]{reads \\ aligning \\ to SARS2} & \makecell[r]{ total pre-\\processed \\ reads} \\ 

@@

 Overall, there were SARS-CoV-2 reads in just 3 of the 28 samples with at least 20\% of their chordate mitochondrial composition from the non-human susceptible species thought to have been sold live in the market (Table~\ref{tab:susceptible}).
There were 14 samples with at least 20\% chordate mitochondrial composition from raccoon dogs, but only sample Q61 contained any SARS-CoV-2 reads (1 of $\sim2.1 \times 10^8$ high-quality reads).
None of the six samples with at least 20\% chordate mitochondrial composition from bamboo rats contained any SARS-CoV-2 reads.
There was one sample each with at least 20\% chordate mitochondrial composition from Amur hedgehog and Malayan porcupine that contained SARS-CoV-2 reads (Table~\ref{tab:susceptible}).
If mitochondrial composition is instead analyzed only among mammals rather than chordates, Q61 is still the only sample with at least 20\% raccoon dog composition that contains any SARS-CoV-2 reads (Table~\ref{tab:susceptible_mammal}).
There is one sample with at least 20\% of its mammalian (but not chordate) mitochondrial composition from bamboo rat that contains a small number of SARS-CoV-2 reads (Table~\ref{tab:susceptible_mammal}).

Note that the 20\% cutoff applied in Tables~\ref{tab:susceptible} and \ref{tab:susceptible_mammal} is not integral to the analysis, but is just a way to subset on samples containing the most material from the species of interest to make the tables small enough to easily visualize.
See Tables~\ref{tab:raccoon_dog_long} and \ref{tab:mito_composition_by_sample} for much larger tables that show comparable data for all samples with respect to the raccoon dog or overall mitochondrial composition, respectively.
For instance, Table~\ref{tab:raccoon_dog_long} shows that there are a few samples with lower raccoon dog mitochondrial composition that also contain some SARS-CoV-2 reads.
However, ultimately these very large tables are difficult to visualize, and so the relationship between SARS-CoV-2 and mitochondrial content for each species for all samples is probably more facilely visualized using the interactive versions of the scatter plots described in the next subsection.

@@

Reads mapping to SARS-CoV-2 out of all high-quality (pre-processed) reads for samples with $\ge$20\% of their mammalian mitochondrial composition from a susceptible non-human species as defined in \citet{crits2023genetic}.
See Table~\ref{tab:susceptible} for a similar table that shows chordate rather than mammalian composition.
This table uses a 20\% cutoff due to space considerations; to see similar data tabulated for all samples with no cutoff, see the much larger Table~\ref{tab:raccoon_dog_long} (for raccoon dog) and Table~\ref{tab:mito_composition_by_sample} (for all species).
\label{tab:susceptible_mammal}
species      &   sample              & \makecell[r]{mammalian \\ mitochondrial \\ reads from \\ species} &  \makecell[r]{reads \\ aligning \\ to SARS2} & \makecell[r]{ total pre-\\processed \\ reads} \\ 
\multirow{28}{*}{raccoon dog} & HJ200050-20200112-1 &                                       94\% &                        0 &                     1e+08 \\
                  & HJ200023-20200112-1 &                                       93\% &                        0 &                   6.9e+07 \\
                  & HJ200048-20200112-1 &                                       92\% &                        0 &                   1.2e+08 \\
                  & HJ200019-20200112-1 &                                       90\% &                        0 &                     7e+07 \\
                  & {\bf Q61} &                                       {\bf 81\%} &                        {\bf 1} &                   {\bf 2.1e+08} \\
                  & HJ200017-20200112-1 &                                       81\% &                        0 &                   1.1e+08 \\
                  & 629-3-C &                                       78\% &                        0 &                   2.5e+08 \\
                  & HJ200044-20200112-1 &                                       76\% &                        0 &                   1.2e+08 \\
                  & HJ200014-20200112-1 &                                       70\% &                        0 &                   1.1e+08 \\
                  & HJ200047-20200112-1 &                                       66\% &                        0 &                   1.4e+08 \\
                  & HJ200011-20200112-1 &                                       61\% &                        0 &                   5.8e+07 \\
                  & HJ200018-20200112-1 &                                       53\% &                        0 &                   1.4e+08 \\
                  & HJ200013-20200112-1 &                                       50\% &                        0 &                   1.1e+08 \\
                  & HJ200012-20200112-1 &                                       50\% &                        0 &                   1.3e+08 \\
                  & HJ200043-20200112-1 &                                       48\% &                        0 &                   8.3e+07 \\
                  & HJ200027-20200112-1 &                                       43\% &                        0 &                     9e+07 \\
                  & HJ200024-20200112-1 &                                       42\% &                        0 &                   9.8e+07 \\
                  & HJ200001-20200112-1 &                                       38\% &                        0 &                   1.2e+08 \\
                  & HJ200016-20200112-1 &                                       33\% &                        0 &                   1.2e+08 \\
                  & HJ200007-20200112-1 &                                       31\% &                        0 &                   1.4e+08 \\
                  & HJ200020-20200112-1 &                                       31\% &                        0 &                   7.9e+07 \\
                  & HJ200006-20200112-1 &                                       30\% &                        0 &                   1.3e+08 \\
                  & HJ200009-20200112-1 &                                       27\% &                        0 &                   1.5e+08 \\
                  & HJ200045-20200112-1 &                                       27\% &                        0 &                   1.1e+08 \\
                  & HJ200026-20200112-1 &                                       25\% &                        0 &                     1e+08 \\
                  & HJ200022-20200112-1 &                                       23\% &                        0 &                   1.2e+08 \\
                  & HJ200004-20200112-1 &                                       23\% &                        0 &                   2.3e+08 \\
                  & HJ200065-20200112-1 &                                       22\% &                        0 &                   7.3e+07 \\
\multirow{14}{*}{hoary bamboo rat} & 629-13-L &                                       85\% &                        0 &                   1.5e+08 \\
                  & HJ200041-20200112-1 &                                       56\% &                        0 &                   1.8e+08 \\
                  & HJ200015-20200112-1 &                                       56\% &                        0 &                   1.4e+08 \\
                  & HJ200065-20200112-1 &                                       56\% &                        0 &                   7.3e+07 \\
                  & 629-1-L1 &                                       55\% &                        0 &                   2.5e+08 \\
                  & 629-5-L4 &                                       54\% &                        0 &                   1.4e+08 \\
                  & HJ200062-20200112-1 &                                       42\% &                        0 &                   1.8e+08 \\
                  & HJ200013-20200112-1 &                                       37\% &                        0 &                   1.1e+08 \\
                  & HJ200049-20200112-1 &                                       31\% &                        0 &                     1e+08 \\
                  & HJ200046-20200112-1 &                                       28\% &                        0 &                   1.1e+08 \\
                  & HJ200030-20200112-1 &                                       28\% &                        0 &                   1.1e+08 \\
                  & HJ200067-20200112-1 &                                       27\% &                        0 &                   7.7e+07 \\
                  & HJ200025-20200112-1 &                                       21\% &                        0 &                   1.2e+08 \\
                  & {\bf Q68} &                                       {\bf 20\%} &                        {\bf 6} &                   {\bf 8.7e+07} \\
\multirow{15}{*}{Amur hedgehog} & W-8-25-L2 &                                       76\% &                        0 &                   3.1e+08 \\
                  & HJ200040-20200112-1 &                                       75\% &                        0 &                   1.5e+08 \\
                  & HJ200038-20200112-1 &                                       63\% &                        0 &                     1e+08 \\
                  & HJ200039-20200112-1 &                                       62\% &                        0 &                   1.2e+08 \\
                  & 8-25-CK &                                       62\% &                        0 &                   1.5e+09 \\
                  & W-8-25-L &                                       59\% &                        0 &                   2.9e+08 \\
                  & HJ200035-20200112-1 &                                       59\% &                        0 &                   7.2e+07 \\
                  & {\bf 8-25-M1} &                                      {\bf 53\%} &                      {\bf 24} &                   {\bf 4.4e+08} \\
                  & HJ200033-20200112-1 &                                       51\% &                        0 &                   1.2e+08 \\
                  & W-8-25-D2 &                                       50\% &                        0 &                   3.3e+08 \\
                  & W-8-25-D1 &                                       50\% &                        0 &                   2.9e+08 \\
                  & HJ200045-20200112-1 &                                       41\% &                        0 &                   1.1e+08 \\
                  & HJ200032-20200112-1 &                                       35\% &                        0 &                   1.4e+08 \\
                  & 8-25-M2 &                                       24\% &                        0 &                   1.6e+09 \\
                  & HJ200036-20200112-1 &                                       21\% &                        0 &                   2.2e+08 \\
\multirow{2}{*}{Malayan porcupine} & {\bf Q70} &                                      {\bf 93\%} &                       {\bf 2} &                  {\bf 1.5e+08} \\
                  & HJ200001-20200112-1 &                                       23\% &                        0 &                   1.2e+08 \\
Himalayan marmot & HJ200005-20200112-1 &                                       36\% &                        0 &                   1.2e+08 \\
masked palm civet & HJ200042-20200112-1 &                                       22\% &                        0 &                   1.9e+08 \\

\begin{table}
\caption{
See \url{https://github.com/jbloom/Huanan_market_samples/blob/main/results/plots/raccoon_dog_long.csv} for a table giving the raccoon dog mitochondrial composition (both among chordates and mammals) along with the SARS-CoV-2 content for all samples.
\label{tab:raccoon_dog_long}
}
\end{table}
